---
title: "Candidacy: Generate data for APIM"
author: "Julianna Calabrese"
date: "December 21st, 2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Prepwork

```{r}
set.seed(1227)
setwd("/Users/Julianna/OneDrive - The Ohio State University/candidacy/data_analysis")
```

```{r}
library(tidyverse)
library(mice)
library(simsem)
library(lavaan)
library(haven)
library(miceadds)
library(parameters)
library(semTools)
library(readr)
library(sjPlot)
options(scipen = 99999)
```

# List the variables you want

## Good variable names

```{r}
source("0_data/preprocessed/scale_help.R")

meta <- read.csv("0_data/raw/FFMetadata_v09.csv") %>%
  mutate(wave = gsub(" ", "", wave, fixed = TRUE)) %>%
  mutate(respondent = gsub(" ", "", respondent, fixed = TRUE)) %>%
  filter(!source == "restricted") %>%
  filter(!grepl("INT CHK", qtext))

# Demographic variables
demo <- meta %>%
  filter(new_name %in% dhere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()
  
# Coparenting
cop <- meta %>% 
  filter(new_name %in% cophere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()

# Parent Depression
dep <- meta %>%
  filter(new_name %in% dephere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()

keep_these <- append(demo, cop)
keep_these <- append(keep_these, dep)
id <- c("idnum")

keep_these <- append(keep_these, id)
keep_these <- flatten(keep_these)
rm(id, cop, dep, demo, dhere, dephere, cophere)

keep_these <- as.character(keep_these)
```

## Actual variable names

```{r}
source("0_data/preprocessed/scale_help.R")

meta <- read.csv("0_data/raw/FFMetadata_v09.csv") %>%
  mutate(wave = gsub(" ", "", wave, fixed = TRUE)) %>%
  mutate(respondent = gsub(" ", "", respondent, fixed = TRUE)) %>%
  filter(!source == "restricted") %>%
  filter(!grepl("INT CHK", qtext))

# Demographic variables
demo <- meta %>%
  filter(new_name %in% dhere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()
  
# Coparenting
cop <- meta %>% 
  filter(new_name %in% cophere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()

# Parent Depression
dep <- meta %>%
  filter(new_name %in% dephere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()

keep_these2 <- append(demo, cop)
keep_these2 <- append(keep_these2, dep)
id <- c("idnum")

keep_these2 <- append(keep_these2, id)
keep_these2 <- flatten(keep_these2)
rm(id, cop, dep, demo, dhere, dephere, cophere)

keep_these2 <- as.character(keep_these2)
```

```{r}
ref_df <- data.frame(keep_these, keep_these2)
rm(meta, keep_these)
```

# Read and subset data

```{r}
# Master FFCWS dataset
raw <- haven::read_sav(file = "0_data/raw/FF_allwaves_2020v2_SPSS.sav", user_na = TRUE) %>%
  as.data.frame()

df <- raw %>%
  select(any_of(keep_these2)) %>%
  mutate(across(everything(), ~ replace(., . < 0, NA))) %>%
  select(idnum, everything())
```

# Fix the variables name here

"Fix" is a subjective term here. I still maintain the weird FFCWS variable naming scheme, but at least now the variable names include who completed the questionnaire and what year it was completed. This is important because the variable label does not include this information.

```{r}
ref_df <- ref_df %>%
  rename(newnames = keep_these) %>%
  rename(oldnames = keep_these2)

newnames <- ref_df$newnames 
oldnames <- ref_df$oldnames 

df <- df %>%
   rename_with(.fn = ~ newnames,
               .cols = oldnames)

rm(oldnames, newnames)
```

# Additional cleaning here

This is where you would rename variables, convert from long to wide, make sum scores, etc. You can also make the dataset smaller by removing variable that you know you won't need.

You will likely want to remove participants that have a certain percentage of missing values since the current dataset has a lot of `NA`s. Also definitely turn all negative numbers into `NA`.

```{r}
# Remove other years in case they sneak in
df <- df %>% select(!contains("_Year1")) %>% select(!contains("_Year3")) %>% select(!contains("_Year9"))

# Make all negative values NA
# Make everything above 99 for the survey data NA
df <- df %>%
  mutate(across(where(is.double), as.numeric)) %>%
  mutate(across(contains("_Baseline"), ~ replace(., . < 0, NA))) %>%
  mutate(across(contains("_Baseline"), ~ replace(., . > 99, NA))) %>%
  mutate(across(contains("_Year5"), ~ replace(., . < 0, NA))) %>%
  mutate(across(contains("_Year5"), ~ replace(., . > 99, NA)))
```

# How much is missing?

```{r}
# Overall
a <- sum(is.na(df))
b <- sum(is.na(df)) + sum(!is.na(df))
allmiss <- a/b
rm(a,b)

# Mother
x <- df %>% select(starts_with("m"))
a <- sum(is.na(x))
b <- sum(is.na(x)) + sum(!is.na(x))
mothermiss <- a/b
rm(a,b,x)

# Father
x <- df %>% select(starts_with("f"))
a <- sum(is.na(x))
b <- sum(is.na(x)) + sum(!is.na(x))
fathermiss <- a/b
rm(a,b,x)

apimmiss <- data.frame(allmiss, fathermiss, mothermiss) %>% 
  t() %>% as.data.frame() %>% rownames_to_column() %>%
  rename(var_type = rowname) %>% rename(amount_missing = V1)

write.csv(apimmiss, "0_data/processed_apim/what_is_missing_apim.csv", row.names = FALSE)
rm(apimmiss)
```

```{r}
rm(list=setdiff(ls(), "df"))
```

# Remove if everything is missing and save IDs to list

```{r}
# Goal: remove if all of data is missing for Year 5

# Make dataframe of bad IDs
who_gets_removed <- df %>% 
  filter(if_all(contains("_Year5"), is.na)) %>%
  select(idnum)

# Save bad IDs
write.table(who_gets_removed, "2_output/remove_me.txt", col.names = FALSE, row.names = FALSE)

# Read back in the character
remove_me <- read.table("2_output/remove_me.txt", 
                        col.names = "idnum",
                        colClasses = "character")

# Actually remove people using character
df <- df %>%
  filter(!(idnum %in% remove_me$idnum))

# Clean up
rm(who_gets_removed, remove_me)
```

# Rename and remove some variables

```{r}
# Coparent
df <- df %>%
  rename_all(str_replace_all, "(f4d1)", "Coparent") %>%
  rename_all(str_replace_all, "(m4d1)", "Coparent")

# Depression
df <- df %>%
  rename_all(str_replace_all, "(f4j)", "Depression") %>%
  rename_all(str_replace_all, "(m4j)", "Depression")
```

```{r}
# Coparent Rename
df <- df %>%
  rename_all(str_replace_all, "(Coparenta_)", "Coparent_item1_") %>%
  rename_all(str_replace_all, "(Coparentb_)", "Coparent_item2_") %>%
  rename_all(str_replace_all, "(Coparentc_)", "Coparent_item3_") %>%
  rename_all(str_replace_all, "(Coparentd_)", "Coparent_item4_") %>%
  rename_all(str_replace_all, "(Coparente_)", "Coparent_item5_") %>%
  rename_all(str_replace_all, "(Coparentf_)", "Coparent_item6_") %>%
  rename_all(str_replace_all, "(Coparentg_)", "Coparent_item7_") %>%
  rename_all(str_replace_all, "(Coparenth_)", "Coparent_item8_")
``` 

```{r}
# Depression Rename
df <- df %>%
  rename_all(str_replace_all, "(Depression5_)", "Depression_Criteria_") %>%
  rename_all(str_replace_all, "(Depression6_)", "Depression_HowMuchOfDay_") %>%
  rename_all(str_replace_all, "(Depression7_)", "Depression_HowOften_") %>%
  rename_all(str_replace_all, "(Depression8_)", "Depression_item1_") %>%
  rename_all(str_replace_all, "(Depression9_)", "Depression_HowOften1_") %>%
  rename_all(str_replace_all, "(Depression10_)", "Depression_HowLong1_") %>%
  rename_all(str_replace_all, "(Depression11_)", "Depression_AlmostEveryday1_") %>%
  rename_all(str_replace_all, "(Depression12_)", "Depression_item2_") %>%
  rename_all(str_replace_all, "(Depression13_)", "Depression_LoseGainSameWeight_") %>%
  rename_all(str_replace_all, "(Depression14_)", "Depression_item3_") %>%
  rename_all(str_replace_all, "(Depression15_)", "Depression_item4_") %>%
  rename_all(str_replace_all, "(Depression16_)", "Depression_item5_") %>%
  rename_all(str_replace_all, "(Depression17_)", "Depression_item6_")
```

```{r}
df <- df %>%
  select(!contains("HowMuchOfDay")) %>%
  select(!contains("HowOften")) %>%
  select(!contains("HowLong")) %>%
  select(!contains("AlmostEveryday")) %>%
  select(!contains("LoseGainSameWeight"))
```

```{r}
# Rename the composite scores
# These are binary and were calculated by FFCWS
df <- df %>%
  rename(CompositeDepression_Mother_Lib_Year5 = cm4md_case_lib_Mother_Year5) %>%
  rename(CompositeDepression_Mother_Con_Year5 = cm4md_case_con_Mother_Year5) %>%
  rename(CompositeDepression_Father_Lib_Year5 = cf4md_case_lib_Father_Year5) %>%
  rename(CompositeDepression_Father_Con_Year5 = cf4md_case_con_Father_Year5)

df <- df %>%
    mutate(across(.cols = contains("Composite"), 
                  ~factor(.x)))

df <- df %>%
  select(!contains("Composite"))
```

```{r}
# Don't need these...
df <- df %>%
  select(!contains("f1h2")) %>%
  select(!contains("m1h2"))

df <- df %>%
  mutate(MotherRaceEth_Baseline = as.factor(cm1ethrace_Mother_Baseline)) %>%
  mutate(FatherRaceEth_Baseline = as.factor(cf1ethrace_Father_Baseline))

df <- df %>%
  mutate(MotherRaceEth_String_Baseline = 
           recode(MotherRaceEth_Baseline, 
                  "1" = "White, non-Hispanic",
                  "2" = "Black, non-Hispanic",
                  "3" = "Hispanic",
                  "4" = "Other"))

df <- df %>%
  mutate(FatherRaceEth_String_Baseline = 
           recode(FatherRaceEth_Baseline, 
                  "1" = "White, non-Hispanic",
                  "2" = "Black, non-Hispanic",
                  "3" = "Hispanic",
                  "4" = "Other"))

df <- df %>%
  rename_all(str_replace_all, "(cf1age)", "FathersAge") %>%
  rename_all(str_replace_all, "(cf1edu)", "FathersEdu") %>%
  rename_all(str_replace_all, "(cm1age)", "MothersAge") %>%
  rename_all(str_replace_all, "(cm1edu)", "MothersEdu") %>%
  rename_all(str_replace_all, "(cm1povca)", "MothersPoverty") %>%
  rename_all(str_replace_all, "(cf1povca)", "FathersPoverty")

df <- df %>%
  rename(MotherMarried_Mother_Baseline = cm1marf_Mother_Baseline) %>%
  rename(MotherCohabit_Mother_Baseline = cm1cohf_Mother_Baseline) %>%
  rename(ChildGender_Mother_Baseline = cm1bsex_Mother_Baseline)

# Probably don't need these
df <- df %>%
  select(!contains("f1h3")) %>%
  select(!contains("cf1inpov")) %>%
  select(!contains("cf1eth")) %>%
  select(!contains("cm1eth")) %>%
  select(!contains("relf")) %>%
  select(!contains("m1h3")) %>%
  select(!contains("m1i4"))

# last minute thing...
df <- df %>%
  rename(MotherRace_Mother_Baseline = MotherRaceEth_Baseline) %>%
  rename(FatherRace_Father_Baseline = FatherRaceEth_Baseline) %>%
  rename(MotherRaceString_Mother_Baseline = MotherRaceEth_String_Baseline) %>%
  rename(FatherRaceString_Father_Baseline = FatherRaceEth_String_Baseline)
```

```{r}
df <- df %>%
  select(!contains("String")) %>%
  select(!contains("Gender")) %>%
  select(!contains("Cohabit")) %>%
  select(!contains("Married"))
```

# Reverse code all the coparenting items

```{r}
# df %>% select(starts_with("Coparent")) %>% head(., 5) # View the raw variables

df <- df %>%
    mutate(across(starts_with("Coparent"), ~ # <- the variables that we want to recode
                    recode(., "1" = 4, "2" = 3, "3" = 2, "4" = 1))) # <- desired recoding scheme

# df %>% select(starts_with("Coparent")) %>% head(., 5)  # View the variables again, now they're reversed
```

# Make the depression items 0/1 instead of 1/2

The original FFCWS study has 1 mean Yes and 2 mean No. I want to recode all the items so 0 means No and 1 means Yes.

```{r}
df <- df %>%
  mutate(across(contains("Depression"), 
                ~case_when(.x == 2 ~ 0, 
                           TRUE ~ as.numeric(.x))))
```

# Calculate subscales

```{r}
# Coparenting
df <- df %>%
  rowwise() %>%
  mutate(Coparent_Total_Mother = mean(c(
    Coparent_item1_Mother_Year5,
    Coparent_item2_Mother_Year5,
    Coparent_item3_Mother_Year5,
    Coparent_item4_Mother_Year5,
    Coparent_item5_Mother_Year5,
    Coparent_item6_Mother_Year5
    ), na.rm = TRUE)) %>%
  ungroup()

df <- df %>%
  rowwise() %>%
  mutate(Coparent_Total_Father = mean(c(
    Coparent_item1_Father_Year5,
    Coparent_item2_Father_Year5,
    Coparent_item3_Father_Year5,
    Coparent_item4_Father_Year5,
    Coparent_item5_Father_Year5,
    Coparent_item6_Father_Year5
    ), na.rm = TRUE)) %>%
  ungroup()
```

```{r} 
# Depression
df <- df %>%
  rowwise() %>%
  mutate(Depression_Total_Mother = mean(c(
    Depression_item1_Mother_Year5,
    Depression_item2_Mother_Year5,
    Depression_item3_Mother_Year5,
    Depression_item4_Mother_Year5,
    Depression_item5_Mother_Year5,
    Depression_item6_Mother_Year5
    ), na.rm = TRUE)) %>%
  ungroup()

df <- df %>% 
  mutate(Depression_Total_Mother = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_Total_Mother)) %>%
  mutate(Depression_item1_Mother_Year5 = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_item1_Mother_Year5)) %>%
  mutate(Depression_item2_Mother_Year5 = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_item2_Mother_Year5)) %>%
  mutate(Depression_item3_Mother_Year5 = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_item3_Mother_Year5)) %>%
  mutate(Depression_item4_Mother_Year5 = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_item4_Mother_Year5)) %>%
  mutate(Depression_item5_Mother_Year5 = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_item5_Mother_Year5)) %>%
  mutate(Depression_item6_Mother_Year5 = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_item6_Mother_Year5))

df <- df %>%
  rowwise() %>%
  mutate(Depression_Total_Father = mean(c(
    Depression_item1_Father_Year5,
    Depression_item2_Father_Year5,
    Depression_item3_Father_Year5,
    Depression_item4_Father_Year5,
    Depression_item5_Father_Year5,
    Depression_item6_Father_Year5
    ), na.rm = TRUE)) %>%
  ungroup()

df <- df %>% 
  mutate(Depression_Total_Father = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_Total_Father)) %>%
  mutate(Depression_item1_Father_Year5 = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_item1_Father_Year5)) %>%
  mutate(Depression_item2_Father_Year5 = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_item2_Father_Year5)) %>%
  mutate(Depression_item3_Father_Year5 = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_item3_Father_Year5)) %>%
  mutate(Depression_item4_Father_Year5 = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_item4_Father_Year5)) %>%
  mutate(Depression_item5_Father_Year5 = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_item5_Father_Year5)) %>%
  mutate(Depression_item6_Father_Year5 = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_item6_Father_Year5))
```

```{r}
df$Depression_Criteria_Mother_Year5 <- NULL
df$Depression_Criteria_Father_Year5 <- NULL
```

# Change all characters to factors

Make sure there are no characters in your dataframe, only factors

```{r}
df <- df %>% mutate(across(where(is.character), as.factor))
```

# Make sure everything is the right class

Education should be an ordered factor.

```{r}
sapply(df, class)

df <- df %>%
  mutate(MothersEdu_Mother_Baseline = factor(MothersEdu_Mother_Baseline
                                             , levels = c("1", "2", "3", "4")
                                             )) %>%
  mutate(FathersEdu_Father_Baseline = factor(FathersEdu_Father_Baseline
                                             , levels = c("1", "2", "3", "4")
                                             ))
```

# Fix NaNs

```{r}
df <- df %>%
  mutate(across(everything(), ~replace(., is.nan(.), NA)))
```

# Save original APIM sample

```{r}
write.csv(df, "0_data/processed_apim/original_apim_df.csv", row.names = FALSE)
```

# Write data generation model

```{r}
myapim <- '
                        Coparent_Total_Mother  ~ a1*Depression_Total_Mother
                        Coparent_Total_Father  ~ a2*Depression_Total_Father
                        Coparent_Total_Mother  ~ p12*Depression_Total_Father
                        Coparent_Total_Father  ~ p21*Depression_Total_Mother
                        Depression_Total_Mother ~ mx1*1
                        Depression_Total_Father ~ mx2*1
                        Coparent_Total_Mother ~ my1*1
                        Coparent_Total_Father ~ my2*1
                        Depression_Total_Mother ~~ vx1*Depression_Total_Mother
                        Depression_Total_Father ~~ vx2*Depression_Total_Father
                        Coparent_Total_Mother ~~ vy1*Coparent_Total_Mother
                        Coparent_Total_Father ~~ vy2*Coparent_Total_Father
                        Depression_Total_Father ~~ cx*Depression_Total_Mother
                        Coparent_Total_Father ~~ cy*Coparent_Total_Mother 
  
                        a_diff := a1 - a2
                        p_diff := p12 - p21
                        k1 := p12/a1
                        k2 := p21/a2
                        k_diff := k1 - k2
                        i_diff := my1 - my2
                        a_ave := (a1 + a2)/2
                        p_ave := (p12 + p21)/2
                        i_ave := (my1 +my2)/2
                        sum1 := (p12 + a1)/2
                        sum2 := (p21 + a2)/2
                        cont1 := a1 - p12
                        cont2 := a2 - p21
                        
'
```

```{r}
write_file(myapim, "2_output/myapim.txt")
```

```{r}
# Estimate the model 
apimd <- lavaan::sem(myapim, 
                     data = df,
                     fixed.x = FALSE,
                     missing = "default")

# Examine the model
original_apim_model <- summary(apimd, fit.measures = TRUE)
options(width = 100)
capture.output(original_apim_model, file = "2_output/apim/original_apim_model.txt")
```

# Make several predictor matrices

## Matrix 1

Ignore parent gender.

```{r}
imp <- mice(df, maxit = 0, printFlag = FALSE)
pred1 <- imp$pred
meth1 <- imp$meth

pred1 <- as.data.frame(imp$pred)
pred1[pred1==1] <- 0

covariates <- df %>% select(
  contains("Age") |
    contains("Edu") | 
    contains("Poverty") | 
    contains("Race")) %>% names()

pred1 <- pred1 %>%
  as.data.frame() %>%
  rownames_to_column("rownames") %>%
  mutate(rownames = as.character(rownames))

column_names <- pred1 %>% select(-c(rownames)) %>% colnames()

pred1 <- pred1 %>%
  mutate(across(starts_with("Coparent"), ~ if_else(str_starts(rownames, "Coparent"), 1, 0))) %>%
  mutate(across(starts_with("Depression"), ~ if_else(str_starts(rownames, "Depression"), 1, 0)))

# Make covariates a pred1ictor for everything
pred1[,c(covariates)] <- 1

# Subscale total rows should all be 1
pred1 <- pred1 %>% 
  mutate(across(c(where(is.numeric), 
                  -c(idnum, rownames)), ~ 
                  case_when(str_detect(rownames, "Total") ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

# Remove the `rownames` variable
pred1 <- pred1 %>% remove_rownames %>% column_to_rownames(var="rownames")

# Make sure nothing predicts itself
pred1[cbind(seq_len(nrow(pred1)), match(rownames(pred1), colnames(pred1)))] <- 0

# Make a matrix
pred1 <- as.matrix(pred1)
rm(covariates_father, covariates_mother, column_names)

meth1["Coparent_Total_Mother"] <- "~I((Coparent_item1_Mother_Year5 + Coparent_item2_Mother_Year5 + Coparent_item3_Mother_Year5 + Coparent_item4_Mother_Year5 + Coparent_item5_Mother_Year5 + Coparent_item6_Mother_Year5)/6)"

meth1["Coparent_Total_Father"] <- "~I((Coparent_item1_Father_Year5 + Coparent_item2_Father_Year5 + Coparent_item3_Father_Year5 + Coparent_item4_Father_Year5 + Coparent_item5_Father_Year5 + Coparent_item6_Father_Year5)/6)"

meth1["Depression_Total_Mother"] <- "~I((Depression_item1_Mother_Year5 + Depression_item2_Mother_Year5 + Depression_item3_Mother_Year5 + Depression_item4_Mother_Year5 + Depression_item5_Mother_Year5 + Depression_item6_Mother_Year5)/6)"

meth1["Depression_Total_Father"] <- "~I((Depression_item1_Father_Year5 + Depression_item2_Father_Year5 + Depression_item3_Father_Year5 + Depression_item4_Father_Year5 + Depression_item5_Father_Year5 + Depression_item6_Father_Year5)/6)"
```

## Matrix 2

Account for parent gender.

```{r}
imp <- mice(df, maxit = 0, printFlag = FALSE)
pred2 <- imp$pred
meth2 <- imp$meth

pred2 <- as.data.frame(imp$pred)
pred2[pred2==1] <- 0

covariates_mother <- df %>% select(
  contains("Age") |
    contains("Edu") | 
    contains("Poverty") | 
    contains("Race")) %>%
  select(contains("Mother")) %>% names()

covariates_father <- df %>% select(
  contains("Age") |
    contains("Edu") | 
    contains("Poverty") | 
    contains("Race")) %>%
  select(contains("Father")) %>% names()

pred2 <- pred2 %>%
  as.data.frame() %>%
  rownames_to_column("rownames") %>%
  mutate(rownames = as.character(rownames))

column_names <- pred2 %>% select(-c(rownames)) %>% colnames()

pred2 <- pred2 %>%
  mutate(across( (contains("Coparent") & contains("Father")), 
                 ~ if_else( 
                   (str_detect(rownames, "Coparent") & str_detect(rownames, "Father")), 1, 0))) %>%
  mutate(across( (contains("Coparent") & contains("Mother")), 
                 ~ if_else( 
                   (str_detect(rownames, "Coparent") & str_detect(rownames, "Mother")), 1, 0))) %>%
  mutate(across( (contains("Depression") & contains("Father")), 
                 ~ if_else( 
                   (str_detect(rownames, "Depression") & str_detect(rownames, "Father")), 1, 0))) %>%
  mutate(across( (contains("Depression") & contains("Mother")), 
                 ~ if_else( 
                   (str_detect(rownames, "Depression") & str_detect(rownames, "Mother")), 1, 0)))

# Make covariates a predictor for everything but also split by parent gender!
pred2 <- pred2 %>%
  mutate(across(all_of(covariates_father), ~ case_when(str_detect(rownames, "Father") ~ 1,
                                                        TRUE ~ as.numeric(as.character(.))))) %>%
  mutate(across(c(contains("Father")), ~ 
                  case_when( (str_detect(rownames, "Father")) ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

pred2 <- pred2 %>%
  mutate(across(all_of(covariates_mother), ~ case_when(str_detect(rownames, "Mother") ~ 1,
                                                        TRUE ~ as.numeric(as.character(.))))) %>%
  mutate(across(c(contains("Mother")), ~ 
                  case_when( (str_detect(rownames, "Mother")) ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

# Subscale total rows should all be 1, but we need to also split this by parent gender!
pred2 <- pred2 %>% 
  mutate(across(contains("Father"), 
                ~ case_when(str_detect(rownames, "Total") & str_detect(rownames, "Father") ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

pred2 <- pred2 %>% 
  mutate(across(contains("Mother"), 
                ~ case_when(str_detect(rownames, "Total") & str_detect(rownames, "Mother") ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

pred2 <- pred2 %>% remove_rownames %>% column_to_rownames(var="rownames")

# Make sure nothing predicts itself
pred2[cbind(seq_len(nrow(pred2)), match(rownames(pred2), colnames(pred2)))] <- 0

# Make a matrix
pred2 <- as.matrix(pred2)
rm(covariates, column_names)

meth2["Coparent_Total_Mother"] <- "~I((Coparent_item1_Mother_Year5 + Coparent_item2_Mother_Year5 + Coparent_item3_Mother_Year5 + Coparent_item4_Mother_Year5 + Coparent_item5_Mother_Year5 + Coparent_item6_Mother_Year5)/6)"

meth2["Coparent_Total_Father"] <- "~I((Coparent_item1_Father_Year5 + Coparent_item2_Father_Year5 + Coparent_item3_Father_Year5 + Coparent_item4_Father_Year5 + Coparent_item5_Father_Year5 + Coparent_item6_Father_Year5)/6)"

meth2["Depression_Total_Mother"] <- "~I((Depression_item1_Mother_Year5 + Depression_item2_Mother_Year5 + Depression_item3_Mother_Year5 + Depression_item4_Mother_Year5 + Depression_item5_Mother_Year5 + Depression_item6_Mother_Year5)/7)"

meth2["Depression_Total_Father"] <- "~I((Depression_item1_Father_Year5 + Depression_item2_Father_Year5 + Depression_item3_Father_Year5 + Depression_item4_Father_Year5 + Depression_item5_Father_Year5 + Depression_item6_Father_Year5)/7)"
```

# Make template for missingness

```{r}
make_missing <- simsem::miss(
  package = "mice",
  m = 15,
  maxit = 30, 
  seed = 1227,
  # pmMCAR = .15, # how much missing?
  pmMAR = .15, # how much is missing?
  ignoreCols = "idnum",
  convergentCutoff = 0.75)
```

# Generate datasets of different sizes

```{r}
small <- simsem::sim(
  nRep = 1,
  model = apimd,
  n = 200,
  rawData = df,
  # miss = make_missing,
  objMissing = make_missing,
  lavaanfun = "sem",
  modelBoot = TRUE,
  seed = 1227,
  dataOnly = TRUE) %>% as.data.frame()

medium <- simsem::sim(
  nRep = 1,
  model = apimd,
  n = 500,
  rawData = df,
  # miss = make_missing,
  objMissing = make_missing,
  lavaanfun = "sem",
  modelBoot = TRUE,
  seed = 1227,
  dataOnly = TRUE) %>% as.data.frame()

large <- simsem::sim(
  nRep = 1,
  model = apimd,
  n = 2000,
  rawData = df,
  # miss = make_missing,
  objMissing = make_missing,
  lavaanfun = "sem",
  modelBoot = TRUE,
  seed = 1227,
  dataOnly = TRUE) %>% as.data.frame()

rm(make_missing)
```

# Write out raw simulated data

```{r}
write.csv(small, "0_data/processed_apim/small.csv")
write.csv(medium, "0_data/processed_apim/medium.csv")
write.csv(large, "0_data/processed_apim/large.csv")
```

# Save copies of the datasets that include subscale totals for quickpred() imputation

```{r}
small2 <- small
medium2 <- medium
large2 <- large
```

# Fix the overwriting issue with multiply imputed objects

```{r}
rm(df)

small$Depression_Total_Mother <- NA
small$Depression_Total_Father <- NA
small$Coparent_Total_Mother <- NA
small$Coparent_Total_Father <- NA

medium$Depression_Total_Mother <- NA
medium$Depression_Total_Father <- NA
medium$Coparent_Total_Mother <- NA
medium$Coparent_Total_Father <- NA

large$Depression_Total_Mother <- NA
large$Depression_Total_Father <- NA
large$Coparent_Total_Mother <- NA
large$Coparent_Total_Father <- NA
```

# Conduct multiple imputaton

```{r}
setwd("/Users/Julianna/OneDrive - The Ohio State University/candidacy/data_analysis/0_data/processed_apim")
```

## Matrix 1

```{r}
small.mi1 <- mice::mice(small, 
                       m = 15,
                       maxit = 30,
                       method = meth1,
                       seed = 1227,
                       pred = pred1)

write.mice.imputation(mi.res = small.mi1, name = "small.mi1", mids2spss = F)
small.mi1 <- miceadds::mids2datlist(small.mi1)

medium.mi1 <- mice::mice(medium, 
                       m = 15,
                       maxit = 30,
                       method = meth1,
                       seed = 1227,
                       pred = pred1)

write.mice.imputation(mi.res = medium.mi1, name = "medium.mi1", mids2spss = F)
medium.mi1 <- miceadds::mids2datlist(medium.mi1)

large.mi1 <- mice::mice(large, 
                       m = 15,
                       maxit = 30,
                       method = meth1,
                       seed = 1227,
                       pred = pred1)

write.mice.imputation(mi.res = large.mi1, name = "large.mi1", mids2spss = F)
large.mi1 <- miceadds::mids2datlist(large.mi1)
```

## Matrix 2

```{r}
small.mi2 <- mice::mice(small, 
                       m = 15,
                       maxit = 30,
                       method = meth2,
                       seed = 1227,
                       pred = pred2)

write.mice.imputation(mi.res = small.mi2, name = "small.mi2", mids2spss = F)
small.mi2 <- miceadds::mids2datlist(small.mi2)

medium.mi2 <- mice::mice(medium, 
                       m = 15,
                       maxit = 30,
                       method = meth2,
                       seed = 1227,
                       pred = pred2)

write.mice.imputation(mi.res = medium.mi2, name = "medium.mi2", mids2spss = F)
medium.mi2 <- miceadds::mids2datlist(medium.mi2)

large.mi2 <- mice::mice(large, 
                       m = 15,
                       maxit = 30,
                       method = meth2,
                       seed = 1227,
                       pred = pred2)

write.mice.imputation(mi.res = large.mi2, name = "large.mi2", mids2spss = F)
large.mi2 <- miceadds::mids2datlist(large.mi2)
```

## Matrix 3

AKA no method or predictor matrix! Or a very simple predictor matrix.

```{r}
smallquick <- quickpred(small2, mincor = 0.2, method = "pearson")
small.mi3 <- mice::mice(small2, 
                       m = 15,
                       maxit = 30,
                       pred = smallquick,
                       seed = 1227)

write.mice.imputation(mi.res = small.mi3, name = "small.mi3", mids2spss = F)
small.mi3 <- miceadds::mids2datlist(small.mi3)

mediumquick <- quickpred(medium2, mincor = 0.2, method = "pearson")
medium.mi3 <- mice::mice(medium2, 
                       m = 15,
                       maxit = 30,
                       pred = mediumquick,
                       seed = 1227)

write.mice.imputation(mi.res = medium.mi3, name = "medium.mi3", mids2spss = F)
medium.mi3 <- miceadds::mids2datlist(medium.mi3)

largequick <- quickpred(large2, mincor = 0.2, method = "pearson")
large.mi3 <- mice::mice(large2, 
                       m = 15,
                       maxit = 30,
                       pred = largequick,
                       seed = 1227)

write.mice.imputation(mi.res = large.mi3, name = "large.mi3", mids2spss = F)
large.mi3 <- miceadds::mids2datlist(large.mi3)
```
