---
title: "Candidacy: Generate data for emotion dysregulation analyses"
author: "Julianna Calabrese"
date: "January 10th, 2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Prepwork

```{r}
set.seed(1227)
setwd("/Users/calabrese.75/OneDrive - The Ohio State University/candidacy/data_analysis")
```

```{r}
library(tidyverse)
library(mice)
library(simsem)
library(lavaan)
library(haven)
library(miceadds)
library(parameters)
library(semTools)
library(readr)
library(sjPlot)
options(scipen = 99999)
```

# List the variables you want

## Good variable names

```{r}
source("0_data/preprocessed/scale_help.R")

meta <- read.csv("0_data/raw/FFMetadata_v09.csv") %>%
  mutate(wave = gsub(" ", "", wave, fixed = TRUE)) %>%
  mutate(respondent = gsub(" ", "", respondent, fixed = TRUE)) %>%
  filter(!source == "restricted") %>%
  filter(!grepl("INT CHK", qtext))

# Demographic variables
demo <- meta %>%
  filter(new_name %in% dhere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()
  
# Coparenting
cop <- meta %>% 
  filter(new_name %in% cophere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()

# Parent Depression
dep <- meta %>%
  filter(new_name %in% dephere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()

# Children's Behavior Problems
cbcl <- meta %>%
  filter(new_name %in% cbclhere) %>%
  select(new_name, wave, respondent) %>%
  unite(new_name, c(new_name, respondent, wave), sep = "_", remove = FALSE) %>%
  select(new_name) %>%
  as.list()

keep_these <- append(demo, cop)
keep_these <- append(keep_these, dep)
keep_these <- append(keep_these, cbcl)
id <- c("idnum")

keep_these <- append(keep_these, id)
keep_these <- flatten(keep_these)
rm(id, cop, dep, demo, cbcl, dhere, dephere, cbclhere, cophere)

keep_these <- as.character(keep_these)
```

## Actual variable names

```{r}
source("0_data/preprocessed/scale_help.R")

meta <- read.csv("0_data/raw/FFMetadata_v09.csv") %>%
  mutate(wave = gsub(" ", "", wave, fixed = TRUE)) %>%
  mutate(respondent = gsub(" ", "", respondent, fixed = TRUE)) %>%
  filter(!source == "restricted") %>%
  filter(!grepl("INT CHK", qtext))

# Demographic variables
demo <- meta %>%
  filter(new_name %in% dhere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()
  
# Coparenting
cop <- meta %>% 
  filter(new_name %in% cophere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()

# Parent Depression
dep <- meta %>%
  filter(new_name %in% dephere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()

# Children's Behavior Problems
cbcl <- meta %>%
  filter(new_name %in% cbclhere) %>%
  select(new_name, wave, respondent) %>%
  select(new_name) %>%
  as.list()

keep_these2 <- append(demo, cop)
keep_these2 <- append(keep_these2, dep)
keep_these2 <- append(keep_these2, cbcl)
id <- c("idnum")

keep_these2 <- append(keep_these2, id)
keep_these2 <- flatten(keep_these2)
rm(id, cop, dep, demo, cbcl, dhere, dephere, cbclhere, cophere)

keep_these2 <- as.character(keep_these2)
```

```{r}
ref_df <- data.frame(keep_these, keep_these2)
rm(meta, keep_these)
```

# Read and subset data

```{r}
# Master FFCWS dataset
raw <- haven::read_sav(file = "0_data/raw/FF_allwaves_2020v2_SPSS.sav", user_na = TRUE) %>%
  as.data.frame()

df <- raw %>%
  select(any_of(keep_these2)) %>%
  mutate(across(everything(), ~ replace(., . < 0, NA))) %>%
  select(idnum, everything())
```

# Fix the variables name here

"Fix" is a subjective term here. I still maintain the weird FFCWS variable naming scheme, but at least now the variable names include who completed the questionnaire and what year it was completed. This is important because the variable label does not include this information.

```{r}
ref_df <- ref_df %>%
  rename(newnames = keep_these) %>%
  rename(oldnames = keep_these2)

newnames <- ref_df$newnames 
oldnames <- ref_df$oldnames 

df <- df %>%
   rename_with(.fn = ~ newnames,
               .cols = oldnames)

rm(oldnames, newnames)
```

# Additional cleaning here

This is where you would rename variables, convert from long to wide, make sum scores, etc. You can also make the dataset smaller by removing variable that you know you won't need.

You will likely want to remove participants that have a certain percentage of missing values since the current dataset has a lot of `NA`s. Also definitely turn all negative numbers into `NA`.

```{r}
# Remove other years in case they sneak in
df <- df %>% select(!contains("_Year1")) %>% select(!contains("_Year3")) %>% select(!contains("_Year9"))

# Make all negative values NA
# Make everything above 99 for the survey data NA
df <- df %>%
  mutate(across(where(is.double), as.numeric)) %>%
  mutate(across(contains("_Baseline"), ~ replace(., . < 0, NA))) %>%
  mutate(across(contains("_Baseline"), ~ replace(., . > 99, NA))) %>%
  mutate(across(contains("_Year5"), ~ replace(., . < 0, NA))) %>%
  mutate(across(contains("_Year5"), ~ replace(., . > 99, NA)))
```

# How much is missing?

```{r}
# Overall
a <- sum(is.na(df))
b <- sum(is.na(df)) + sum(!is.na(df))
allmiss <- a/b
rm(a,b)

# Mother
x <- df %>% select(starts_with("m"))
a <- sum(is.na(x))
b <- sum(is.na(x)) + sum(!is.na(x))
mothermiss <- a/b
rm(a,b,x)

# Father
x <- df %>% select(starts_with("f"))
a <- sum(is.na(x))
b <- sum(is.na(x)) + sum(!is.na(x))
fathermiss <- a/b
rm(a,b,x)

# PCG
x <- df %>% select(starts_with("p"))
a <- sum(is.na(x))
b <- sum(is.na(x)) + sum(!is.na(x))
pcgmiss <- a/b
rm(a,b,x)

emoregmiss <- data.frame(allmiss, fathermiss, mothermiss, pcgmiss) %>% 
  t() %>% as.data.frame() %>% rownames_to_column() %>%
  rename(var_type = rowname) %>% rename(amount_missing = V1)

write.csv(emoregmiss, "0_data/processed_emoreg/what_is_missing_emoreg.csv", row.names = FALSE)
rm(emoregmiss)
```

```{r}
rm(list=setdiff(ls(), "df"))
```

# Remove if everything is missing

```{r}
# Read back in the character
remove_me <- read.table("2_output/remove_me.txt", 
                        col.names = "idnum",
                        colClasses = "character")

# Actually remove people using character
df <- df %>%
  filter(!(idnum %in% remove_me$idnum))

# Clean up
rm(remove_me)
```

# Rename and remove some variables

```{r}
# Coparent
df <- df %>%
  rename_all(str_replace_all, "(f4d1)", "Coparent") %>%
  rename_all(str_replace_all, "(m4d1)", "Coparent")

# Depression
df <- df %>%
  rename_all(str_replace_all, "(f4j)", "Depression") %>%
  rename_all(str_replace_all, "(m4j)", "Depression")
```

```{r}
# Coparent Rename
df <- df %>%
  rename_all(str_replace_all, "(Coparenta_)", "Coparent_item1_") %>%
  rename_all(str_replace_all, "(Coparentb_)", "Coparent_item2_") %>%
  rename_all(str_replace_all, "(Coparentc_)", "Coparent_item3_") %>%
  rename_all(str_replace_all, "(Coparentd_)", "Coparent_item4_") %>%
  rename_all(str_replace_all, "(Coparente_)", "Coparent_item5_") %>%
  rename_all(str_replace_all, "(Coparentf_)", "Coparent_item6_") %>%
  rename_all(str_replace_all, "(Coparentg_)", "Coparent_item7_") %>%
  rename_all(str_replace_all, "(Coparenth_)", "Coparent_item8_")
``` 

```{r}
# Depression Rename
df <- df %>%
  rename_all(str_replace_all, "(Depression5_)", "Depression_Criteria_") %>%
  rename_all(str_replace_all, "(Depression6_)", "Depression_HowMuchOfDay_") %>%
  rename_all(str_replace_all, "(Depression7_)", "Depression_HowOften_") %>%
  rename_all(str_replace_all, "(Depression8_)", "Depression_item1_") %>%
  rename_all(str_replace_all, "(Depression9_)", "Depression_HowOften1_") %>%
  rename_all(str_replace_all, "(Depression10_)", "Depression_HowLong1_") %>%
  rename_all(str_replace_all, "(Depression11_)", "Depression_AlmostEveryday1_") %>%
  rename_all(str_replace_all, "(Depression12_)", "Depression_item2_") %>%
  rename_all(str_replace_all, "(Depression13_)", "Depression_LoseGainSameWeight_") %>%
  rename_all(str_replace_all, "(Depression14_)", "Depression_item3_") %>%
  rename_all(str_replace_all, "(Depression15_)", "Depression_item4_") %>%
  rename_all(str_replace_all, "(Depression16_)", "Depression_item5_") %>%
  rename_all(str_replace_all, "(Depression17_)", "Depression_item6_")

df <- df %>%
  select(!contains("HowMuchOfDay")) %>%
  select(!contains("HowOften")) %>%
  select(!contains("HowLong")) %>%
  select(!contains("AlmostEveryday")) %>%
  select(!contains("LoseGainSameWeight"))
```

```{r}
# Rename the composite scores
# These are binary and were calculated by FFCWS
df <- df %>%
  rename(CompositeDepression_Mother_Lib_Year5 = cm4md_case_lib_Mother_Year5) %>%
  rename(CompositeDepression_Mother_Con_Year5 = cm4md_case_con_Mother_Year5) %>%
  rename(CompositeDepression_Father_Lib_Year5 = cf4md_case_lib_Father_Year5) %>%
  rename(CompositeDepression_Father_Con_Year5 = cf4md_case_con_Father_Year5)

df <- df %>%
    mutate(across(.cols = contains("Composite"), 
                  ~factor(.x)))

df <- df %>%
  select(!contains("Composite"))
```

```{r}
# CBCL Rename
source("0_data/preprocessed/scale_help.R")
df <- cbcl_rename_function(df)
df <- df %>% select(order(colnames(df))) %>%
  select(idnum, everything())
rm(list=setdiff(ls(), "df"))
```

```{r}
# Don't need these...
df <- df %>%
  select(!contains("f1h2")) %>%
  select(!contains("m1h2"))

df <- df %>%
  mutate(MotherRaceEth_Baseline = as.factor(cm1ethrace_Mother_Baseline)) %>%
  mutate(FatherRaceEth_Baseline = as.factor(cf1ethrace_Father_Baseline))

df <- df %>%
  mutate(MotherRaceEth_String_Baseline = 
           recode(MotherRaceEth_Baseline, 
                  "1" = "White, non-Hispanic",
                  "2" = "Black, non-Hispanic",
                  "3" = "Hispanic",
                  "4" = "Other"))

df <- df %>%
  mutate(FatherRaceEth_String_Baseline = 
           recode(FatherRaceEth_Baseline, 
                  "1" = "White, non-Hispanic",
                  "2" = "Black, non-Hispanic",
                  "3" = "Hispanic",
                  "4" = "Other"))

df <- df %>%
  rename_all(str_replace_all, "(cf1age)", "FathersAge") %>%
  rename_all(str_replace_all, "(cf1edu)", "FathersEdu") %>%
  rename_all(str_replace_all, "(cm1age)", "MothersAge") %>%
  rename_all(str_replace_all, "(cm1edu)", "MothersEdu") %>%
  rename_all(str_replace_all, "(cm1povca)", "MothersPoverty") %>%
  rename_all(str_replace_all, "(cf1povca)", "FathersPoverty")

df <- df %>%
  rename(MotherMarried_Mother_Baseline = cm1marf_Mother_Baseline) %>%
  rename(MotherCohabit_Mother_Baseline = cm1cohf_Mother_Baseline) %>%
  rename(ChildGender_Mother_Baseline = cm1bsex_Mother_Baseline)

# Probably don't need these
df <- df %>%
  select(!contains("f1h3")) %>%
  select(!contains("cf1inpov")) %>%
  select(!contains("cf1eth")) %>%
  select(!contains("cm1eth")) %>%
  select(!contains("relf")) %>%
  select(!contains("m1h3")) %>%
  select(!contains("m1i4"))

# last minute thing...
df <- df %>%
  rename(MotherRace_Mother_Baseline = MotherRaceEth_Baseline) %>%
  rename(FatherRace_Father_Baseline = FatherRaceEth_Baseline) %>%
  rename(MotherRaceString_Mother_Baseline = MotherRaceEth_String_Baseline) %>%
  rename(FatherRaceString_Father_Baseline = FatherRaceEth_String_Baseline)
```

```{r}
df <- df %>%
  select(!contains("String")) %>%
  select(!contains("Gender")) %>%
  select(!contains("Cohabit")) %>%
  select(!contains("Married"))
```

# Reverse code all the coparenting items

```{r}
# df %>% select(starts_with("Coparent")) %>% head(., 5) # View the raw variables

df <- df %>%
    mutate(across(starts_with("Coparent"), ~ # <- the variables that we want to recode
                    recode(., "1" = 4, "2" = 3, "3" = 2, "4" = 1))) # <- desired recoding scheme

# df %>% select(starts_with("Coparent")) %>% head(., 5)  # View the variables again, now they're reversed
```

# Make the depression items 0/1 instead of 1/2

The original FFCWS study has 1 mean Yes and 2 mean No. I want to recode all the items so 0 means No and 1 means Yes.

```{r}
df <- df %>%
  mutate(across(contains("Depression"), 
                ~case_when(.x == 2 ~ 0, 
                           TRUE ~ as.numeric(.x))))

# table(df$Depression1_Father_Year5)
# sum(is.na(df$Depression1_Father_Year5))
# class(df)
```

# Calculate subscales

```{r}
# Coparenting
df <- df %>%
  rowwise() %>%
  mutate(Coparent_Total_Mother = mean(c(
    Coparent_item1_Mother_Year5,
    Coparent_item2_Mother_Year5,
    Coparent_item3_Mother_Year5,
    Coparent_item4_Mother_Year5,
    Coparent_item5_Mother_Year5,
    Coparent_item6_Mother_Year5
    ), na.rm = TRUE)) %>%
  ungroup()

df <- df %>%
  rowwise() %>%
  mutate(Coparent_Total_Father = mean(c(
    Coparent_item1_Father_Year5,
    Coparent_item2_Father_Year5,
    Coparent_item3_Father_Year5,
    Coparent_item4_Father_Year5,
    Coparent_item5_Father_Year5,
    Coparent_item6_Father_Year5
    ), na.rm = TRUE)) %>%
  ungroup()
```

```{r}
# Depression
df <- df %>%
  rowwise() %>%
  mutate(Depression_Total_Mother = mean(c(
    Depression_item1_Mother_Year5,
    Depression_item2_Mother_Year5,
    Depression_item3_Mother_Year5,
    Depression_item4_Mother_Year5,
    Depression_item5_Mother_Year5,
    Depression_item6_Mother_Year5
    ), na.rm = TRUE)) %>%
  ungroup()

df <- df %>% mutate(Depression_Total_Mother = if_else(Depression_Criteria_Mother_Year5 == 0, 0, Depression_Total_Mother))

df <- df %>%
  rowwise() %>%
  mutate(Depression_Total_Father = mean(c(
    Depression_item1_Father_Year5,
    Depression_item2_Father_Year5,
    Depression_item3_Father_Year5,
    Depression_item4_Father_Year5,
    Depression_item5_Father_Year5,
    Depression_item6_Father_Year5
    ), na.rm = TRUE)) %>%
  ungroup()

df <- df %>% mutate(Depression_Total_Father = if_else(Depression_Criteria_Father_Year5 == 0, 0, Depression_Total_Father))

df$Depression_itemCriteria_Mother_Year5 <- NULL
df$Depression_itemCriteria_Father_Year5 <- NULL
```

```{r}
# CBCL
# The Dysregulation Profile is a combination of the Attention,
# Aggression, and Anxiety/Depression subscale
# https://pubmed.ncbi.nlm.nih.gov/26254616/
# I hate the CBCL

df <- df %>%
  rowwise() %>%
  mutate(CBCL_EmoDysreg_Total = mean(c_across(contains("CBCL")), na.rm = TRUE)) %>%
  ungroup()
```

# Change all characters to factors

Make sure there are no characters in your dataframe, only factors

```{r}
df <- df %>% mutate(across(where(is.character), as.factor))
```

# Make sure everything is the right class

Education should be a factor.

```{r}
sapply(df, class)

df <- df %>%
  mutate(MothersEdu_Mother_Baseline = factor(MothersEdu_Mother_Baseline
                                             , levels = c("1", "2", "3", "4")
                                             )) %>%
  mutate(FathersEdu_Father_Baseline = factor(FathersEdu_Father_Baseline
                                             , levels = c("1", "2", "3", "4")
                                             ))
```

# Fix NaNs

```{r}
df <- df %>%
  mutate(across(everything(), ~replace(., is.nan(.), NA)))
```

# Just remove all the depression variables

You *do not* need them.

```{r}
df <- df %>%
  select(!contains("Depression"))
```

# Save original APIM sample

```{r}
write.csv(df, "0_data/processed_emoreg/original_emoreg_df.csv", row.names = FALSE)
```

# Write data generation model

```{r}
myemoreg <- 'CBCL_EmoDysreg_Total ~ Coparent_Total_Mother + Coparent_Total_Father'
```

```{r}
write_file(myemoreg, "2_output/myemoreg.txt")
```

```{r}
# Estimate the model 
emoregd <- lavaan::sem(myemoreg, 
                     data = df,
                     fixed.x = FALSE,
                     missing = "default")

# Examine the model
original_emoregd_model <- summary(emoregd, fit.measures = TRUE)
options(width = 100)
capture.output(original_emoregd_model, file = "2_output/emoreg/original_emoregd_model.txt")
```

# Make several predictor matrices

## Matrix 1

The only defined matrix for emotion regulation -- Matrix 2 is just "no matrix". 

```{r}
imp <- mice(df, maxit = 0, printFlag = FALSE)
pred1 <- imp$pred
meth1 <- imp$meth

pred1 <- as.data.frame(imp$pred)
pred1[pred1==1] <- 0

covariates_mother <- df %>% select(
  contains("Age") |
    contains("Edu") | 
    contains("Poverty") | 
    contains("Race")) %>%
  select(contains("Mother")) %>% names()

covariates_father <- df %>% select(
  contains("Age") |
    contains("Edu") | 
    contains("Poverty") | 
    contains("Race")) %>%
  select(contains("Father")) %>% names()

pred1 <- pred1 %>%
  as.data.frame() %>%
  rownames_to_column("rownames") %>%
  mutate(rownames = as.character(rownames))

column_names <- pred1 %>% select(-c(rownames)) %>% colnames()

pred1 <- pred1 %>%
  mutate(across( (contains("Coparent") & contains("Father")), 
                 ~ if_else( 
                   (str_detect(rownames, "Coparent") & str_detect(rownames, "Father")), 1, 0))) %>%
  mutate(across( (contains("Coparent") & contains("Mother")), 
                 ~ if_else( 
                   (str_detect(rownames, "Coparent") & str_detect(rownames, "Mother")), 1, 0))) %>%
  mutate(across(starts_with("CBCL"), ~ if_else(str_starts(rownames, "CBCL"), 1, 0)))

# Make covariates a predictor for everything but also split by parent gender!
pred1 <- pred1 %>%
  mutate(across(all_of(covariates_father), ~ case_when(str_detect(rownames, "Father") ~ 1,
                                                        TRUE ~ as.numeric(as.character(.))))) %>%
  mutate(across(c(contains("Father")), ~ 
                  case_when( (str_detect(rownames, "Father")) ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

pred1 <- pred1 %>%
  mutate(across(all_of(covariates_mother), ~ case_when(str_detect(rownames, "Mother") ~ 1,
                                                        TRUE ~ as.numeric(as.character(.))))) %>%
  mutate(across(c(contains("Mother")), ~ 
                  case_when( (str_detect(rownames, "Mother")) ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

# Subscale total rows should all be 1, but we need to also split this by parent gender!
pred1 <- pred1 %>% 
  mutate(across(contains("Father"), 
                ~ case_when(str_detect(rownames, "Total") & str_detect(rownames, "Father") ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

pred1 <- pred1 %>% 
  mutate(across(contains("Mother"), 
                ~ case_when(str_detect(rownames, "Total") & str_detect(rownames, "Mother") ~ 1,
                            TRUE ~ as.numeric(as.character(.)))))

pred1 <- pred1 %>% remove_rownames %>% column_to_rownames(var="rownames")

# Make sure nothing predicts itself
pred1[cbind(seq_len(nrow(pred1)), match(rownames(pred1), colnames(pred1)))] <- 0

# Make a matrix
pred1 <- as.matrix(pred1)
rm(covariates, column_names)

meth1["Coparent_Total_Mother"] <- "~I((Coparent_item1_Mother_Year5 + Coparent_item2_Mother_Year5 + Coparent_item3_Mother_Year5 + Coparent_item4_Mother_Year5 + Coparent_item5_Mother_Year5 + Coparent_item6_Mother_Year5)/6)"

meth1["Coparent_Total_Father"] <- "~I((Coparent_item1_Father_Year5 + Coparent_item2_Father_Year5 + Coparent_item3_Father_Year5 + Coparent_item4_Father_Year5 + Coparent_item5_Father_Year5 + Coparent_item6_Father_Year5)/6)"

meth1["CBCL_EmoDysreg_Total"] <- "~I((CBCLAgg1_PrimaryCaregiver_Year5 + CBCLAgg10_PrimaryCaregiver_Year5 + CBCLAgg11_PrimaryCaregiver_Year5 + CBCLAgg12_PrimaryCaregiver_Year5 + CBCLAgg13_Mother_Year5 + CBCLAgg14_PrimaryCaregiver_Year5 + CBCLAgg15_PrimaryCaregiver_Year5 + CBCLAgg16_Mother_Year5 + CBCLAgg17_PrimaryCaregiver_Year5 + CBCLAgg18_PrimaryCaregiver_Year5 + CBCLAgg2_PrimaryCaregiver_Year5 + CBCLAgg3_PrimaryCaregiver_Year5 + CBCLAgg4_Mother_Year5 + CBCLAgg5_PrimaryCaregiver_Year5 + CBCLAgg6_PrimaryCaregiver_Year5 + CBCLAgg7_PrimaryCaregiver_Year5 + CBCLAgg8_PrimaryCaregiver_Year5 + CBCLAgg9_PrimaryCaregiver_Year5 + CBCLAnxDep1_PrimaryCaregiver_Year5 + CBCLAnxDep10_PrimaryCaregiver_Year5 + CBCLAnxDep11_Mother_Year5 + CBCLAnxDep12_PrimaryCaregiver_Year5 + CBCLAnxDep2_Mother_Year5 + CBCLAnxDep3_PrimaryCaregiver_Year5 + CBCLAnxDep4_PrimaryCaregiver_Year5 + CBCLAnxDep5_PrimaryCaregiver_Year5 + CBCLAnxDep6_Mother_Year5 + CBCLAnxDep7_Mother_Year5 + CBCLAnxDep8_PrimaryCaregiver_Year5 + CBCLAnxDep9_PrimaryCaregiver_Year5 + CBCLAtt1_Mother_Year5 + CBCLAtt10_PrimaryCaregiver_Year5 + CBCLAtt11PrimaryCaregiver_Year5 + CBCLAtt2_Mother_Year5 + CBCLAtt3_Mother_Year5 + CBCLAtt4_PrimaryCaregiver_Year5 + CBCLAtt5_PrimaryCaregiver_Year5 + CBCLAtt6_PrimaryCaregiver_Year5 + CBCLAtt8_PrimaryCaregiver_Year5 + CBCLAtt9_PrimaryCaregiver_Year5)/40)"
```

# Make template for missingness

```{r}
make_missing <- simsem::miss(
  package = "mice",
  m = 15,
  maxit = 30, 
  seed = 1227,
  # pmMCAR = .15, # how much missing?
  pmMAR = .15, # how much is missing?
  ignoreCols = "idnum",
  convergentCutoff = 0.75)
```

# Generate datasets of different sizes

```{r}
small <- simsem::sim(
  nRep = 1,
  model = emoregd,
  n = 200,
  rawData = df,
  # miss = make_missing,
  objMissing = make_missing,
  lavaanfun = "sem",
  modelBoot = TRUE,
  seed = 1227,
  dataOnly = TRUE) %>% as.data.frame()

medium <- simsem::sim(
  nRep = 1,
  model = emoregd,
  n = 500,
  rawData = df,
  # miss = make_missing,
  objMissing = make_missing,
  lavaanfun = "sem",
  modelBoot = TRUE,
  seed = 1227,
  dataOnly = TRUE) %>% as.data.frame()

large <- simsem::sim(
  nRep = 1,
  model = emoregd,
  n = 2000,
  rawData = df,
  # miss = make_missing,
  objMissing = make_missing,
  lavaanfun = "sem",
  modelBoot = TRUE,
  seed = 1227,
  dataOnly = TRUE) %>% as.data.frame()

rm(make_missing)
```

```{r}
write.csv(small, "0_data/processed_emoreg/small.csv")
write.csv(medium, "0_data/processed_emoreg/medium.csv")
write.csv(large, "0_data/processed_emoreg/large.csv")
```

# Save copies of the datasets that include subscale totals for quickpred() imputation

```{r}
small2 <- small
medium2 <- medium
large2 <- large
```

# Fix the overwriting issue with multiply imputed objects

```{r}
rm(df)

small$Coparent_Total_Mother <- NA
small$Coparent_Total_Father <- NA
small$CBCL_EmoDysreg_Total <- NA

medium$Coparent_Total_Mother <- NA
medium$Coparent_Total_Father <- NA
medium$CBCL_EmoDysreg_Total <- NA

large$Coparent_Total_Mother <- NA
large$Coparent_Total_Father <- NA
large$CBCL_EmoDysreg_Total <- NA
```

# Conduct multiple imputaton

```{r}
setwd("/Users/calabrese.75/OneDrive - The Ohio State University/candidacy/data_analysis/0_data/processed_emoreg")
```

## Matrix 1

```{r}
small.mi1 <- mice::mice(small, 
                       m = 15,
                       maxit = 30,
                       method = meth1,
                       seed = 1227,
                       pred = pred1)

write.mice.imputation(mi.res = small.mi1, name = "small.mi1", mids2spss = F)
small.mi1 <- miceadds::mids2datlist(small.mi1)

medium.mi1 <- mice::mice(medium, 
                       m = 15,
                       maxit = 30,
                       method = meth1,
                       seed = 1227,
                       pred = pred1)

write.mice.imputation(mi.res = medium.mi1, name = "medium.mi1", mids2spss = F)
medium.mi1 <- miceadds::mids2datlist(medium.mi1)

large.mi1 <- mice::mice(large, 
                       m = 15,
                       maxit = 30,
                       method = meth1,
                       seed = 1227,
                       pred = pred1)

write.mice.imputation(mi.res = large.mi1, name = "large.mi1", mids2spss = F)
large.mi1 <- miceadds::mids2datlist(large.mi1)
```

## Matrix 2

AKA no method or predictor matrix!

```{r}
smallquick <- quickpred(small2, mincor = 0.2, method = "pearson")
small.mi2 <- mice::mice(small2, 
                       m = 15,
                       maxit = 30,
                       pred = smallquick,
                       seed = 1227)

write.mice.imputation(mi.res = small.mi2, name = "small.mi2", mids2spss = F)
small.mi2 <- miceadds::mids2datlist(small.mi2)

mediumquick <- quickpred(medium2, mincor = 0.2, method = "pearson")
medium.mi2 <- mice::mice(medium2, 
                       m = 15,
                       maxit = 30,
                       pred = mediumquick,
                       seed = 1227)

write.mice.imputation(mi.res = medium.mi2, name = "medium.mi2", mids2spss = F)
medium.mi2 <- miceadds::mids2datlist(medium.mi2)

largequick <- quickpred(large2, mincor = 0.2, method = "pearson")
large.mi2 <- mice::mice(large2, 
                       m = 15,
                       maxit = 30,
                       pred = largequick,
                       seed = 1227)

write.mice.imputation(mi.res = large.mi2, name = "large.mi2", mids2spss = F)
large.mi2 <- miceadds::mids2datlist(large.mi2)
```
