---
title: "Candidacy project: Load in data and make SEM output for emotion dysregulation data"
author: "Julianna Calabrese"
date: "January 11th, 2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Prepwork

```{r}
set.seed(1227)
setwd("/Users/calabrese.75/OneDrive - The Ohio State University/candidacy/data_analysis")
```

```{r}
#install.packages("Rtools")
#install.packages(c('devtools', 'curl'))
#library('devtools')
#devtools::install_github("simsem/semTools/semTools")
#install.packages("lavaan", repos = "http://www.da.ugent.be", type = "source")
```

```{r}
library(semTools)
library(lavaan)
library(tidyverse)
library(simsem)
library(mice)
library(miceadds)
library(semPlot)
library(lavaanPlot)
library(officer)
library(psych)
library(rrtable)

library(ggmice)
library(micemd)
library(gtsummary)
library(expss)
library(flextable)
library(devtools)
#install_github("jrcalabrese/missy")
library(missy)

options(scipen = 99999) # avoids scientific notation
```

# Load all mids objects

## Raw and generated datasets

```{r}
small_apim <- read.csv("0_data/processed_apim/small.csv")
medium_apim <- read.csv("0_data/processed_apim/medium.csv")
large_apim <- read.csv("0_data/processed_apim/large.csv")
original_apim <- read.csv("0_data/processed_apim/original_apim_df.csv")

small_emoreg <- read.csv("0_data/processed_emoreg/small.csv")
medium_emoreg <- read.csv("0_data/processed_emoreg/medium.csv")
large_emoreg <- read.csv("0_data/processed_emoreg/large.csv")
original_emoreg <- read.csv("0_data/processed_emoreg/original_emoreg_df.csv")
```

## APIM

```{r}
# Small
load("0_data/processed_apim/small.mi1/small.mi1.Rdata")
apimsmall.mi1 <- mi.res
rm(mi.res)

load("0_data/processed_apim/small.mi2/small.mi2.Rdata")
apimsmall.mi2 <- mi.res
rm(mi.res)

load("0_data/processed_apim/small.mi3/small.mi3.Rdata")
apimsmall.mi3 <- mi.res
rm(mi.res)

# Medium
load("0_data/processed_apim/medium.mi1/medium.mi1.Rdata")
apimmedium.mi1 <- mi.res
rm(mi.res)

load("0_data/processed_apim/medium.mi2/medium.mi2.Rdata")
apimmedium.mi2 <- mi.res
rm(mi.res)

load("0_data/processed_apim/medium.mi3/medium.mi3.Rdata")
apimmedium.mi3 <- mi.res
rm(mi.res)

# Large
load("0_data/processed_apim/large.mi1/large.mi1.Rdata")
apimlarge.mi1 <- mi.res
rm(mi.res)

load("0_data/processed_apim/large.mi2/large.mi2.Rdata")
apimlarge.mi2 <- mi.res
rm(mi.res)

load("0_data/processed_apim/large.mi3/large.mi3.Rdata")
apimlarge.mi3 <- mi.res
rm(mi.res)
```

## Emo Reg

```{r}
# Small
load("0_data/processed_emoreg/small.mi1/small.mi1.Rdata")
emoregsmall.mi1 <- mi.res
rm(mi.res)

load("0_data/processed_emoreg/small.mi2/small.mi2.Rdata")
emoregsmall.mi2 <- mi.res
rm(mi.res)

# Medium
load("0_data/processed_emoreg/medium.mi1/medium.mi1.Rdata")
emoregmedium.mi1 <- mi.res
rm(mi.res)

load("0_data/processed_emoreg/medium.mi2/medium.mi2.Rdata")
emoregmedium.mi2 <- mi.res
rm(mi.res)

# Large
load("0_data/processed_emoreg/large.mi1/large.mi1.Rdata")
emoreglarge.mi1 <- mi.res
rm(mi.res)

load("0_data/processed_emoreg/large.mi2/large.mi2.Rdata")
emoreglarge.mi2 <- mi.res
rm(mi.res)
```

# Raw data statistics

## Demographic data

Too lazy to make a table, I'll just write about in the manuscript.

```{r}
a <- mean(original_apim$MothersAge_Mother_Baseline, na.rm = TRUE)
b <- mean(original_apim$FathersAge_Father_Baseline, na.rm = TRUE)
c <- a + b
c/2

a <- sd(original_apim$MothersAge_Mother_Baseline, na.rm = TRUE)
b <- sd(original_apim$FathersAge_Father_Baseline, na.rm = TRUE)
c <- a + b
c/2

table(original_apim$MotherRace_Mother_Baseline)
table(original_apim$FatherRace_Father_Baseline)

table(original_apim$MothersPoverty_Mother_Baseline)
table(original_apim$FathersPoverty_Father_Baseline)

table(original_apim$MothersEdu_Mother_Baseline)
table(original_apim$FathersEdu_Father_Baseline)

rm(a, b, c, df2)
```

# Descriptive Statistics

## APIM

```{r}
myvars <- c("Coparent_Total_Mother", 
            "Coparent_Total_Father", 
            "Depression_Total_Mother", 
            "Depression_Total_Father")

sect_properties <- prop_section(page_size = page_size(orient = "landscape"))

## Matrix 1
mice_df(apimsmall.mi1, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi1destat.docx", 
               pr_section = sect_properties)

mice_df(apimmedium.mi1, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi1destat.docx", 
               pr_section = sect_properties)

mice_df(apimlarge.mi1, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi1destat.docx", 
               pr_section = sect_properties)

## Matrix 2
mice_df(apimsmall.mi2, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi2destat.docx", 
               pr_section = sect_properties)

mice_df(apimmedium.mi2, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi2destat.docx", 
               pr_section = sect_properties)

mice_df(apimlarge.mi2, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi2destat.docx", 
               pr_section = sect_properties)

## Matrix 3
mice_df(apimsmall.mi3, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi3destat.docx", 
               pr_section = sect_properties)

mice_df(apimmedium.mi3, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi3destat.docx", 
               pr_section = sect_properties)

mice_df(apimlarge.mi3, vs = myvars) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi3destat.docx", 
               pr_section = sect_properties)
```

```{r}
## Non-imputed
small_apim %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(small_apim)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/apim/nonimputed_output/smallapimrawdestat.docx", 
               pr_section = sect_properties)

medium_apim %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(medium_apim)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/apim/nonimputed_output/mediumapimrawdestat.docx", 
               pr_section = sect_properties)
  
large_apim %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(large_apim)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/apim/nonimputed_output/largeapimrawdestat.docx", 
               pr_section = sect_properties)

original_apim %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(original_apim)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/apim/nonimputed_output/originalapimrawdestat.docx", 
               pr_section = sect_properties)
```

## Emo Reg

```{r}
myvars <- c("Coparent_Total_Mother", 
            "Coparent_Total_Father",
            "CBCL_EmoDysreg_Total")

sect_properties <- prop_section(page_size = page_size(orient = "landscape"))

## Matrix 1
mice_df(emoregsmall.mi1, vs = myvars) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi1destat.docx", 
               pr_section = sect_properties)

mice_df(emoregmedium.mi1, vs = myvars) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi1destat.docx", 
               pr_section = sect_properties)

mice_df(emoreglarge.mi1, vs = myvars) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi1destat.docx", 
               pr_section = sect_properties)

## Matrix 2
mice_df(emoregsmall.mi2, vs = myvars) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi2destat.docx", 
               pr_section = sect_properties)

mice_df(emoregmedium.mi2, vs = myvars) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi2destat.docx", 
               pr_section = sect_properties)

mice_df(emoreglarge.mi2, vs = myvars) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi2destat.docx", 
               pr_section = sect_properties)
```

```{r}
## Non-imputed
small_emoreg %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(small_emoreg)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/emoreg/nonimputed_output/smallemoregrawdestat.docx", 
               pr_section = sect_properties)

medium_emoreg %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(medium_emoreg)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/emoreg/nonimputed_output/mediumemoregrawdestat.docx", 
               pr_section = sect_properties)
  
large_emoreg %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(large_emoreg)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/emoreg/nonimputed_output/largeemoregrawdestat.docx", 
               pr_section = sect_properties)

original_emoreg %>%
  select(all_of(myvars)) %>%
  psych::describe(na.rm = FALSE) %>%
  as.data.frame() %>%
  select(mean, sd, min, max, se, n) %>%
  mutate(missing = n - length(original_emoreg)) %>%
  select(-n) %>%
  rownames_to_column(var = "Variable") %>%
  rename(Mean = mean) %>% rename(`Standard Deviation` = sd) %>%
  rename(Minimum = min) %>% rename(Maximum = max) %>%
  rename(`Standard Error` = se) %>%
  rename(`# of Missing Values` = missing) %>%
  rrtable::df2flextable() %>% apa_theme() %>% 
  bg(bg = "white", part = "header") %>%
  save_as_docx(path = "2_output/emoreg/nonimputed_output/originalemoregrawdestat.docx", 
               pr_section = sect_properties)
```

# Cronbach's alpha 

```{r}
## Depression
depression_mom <- small_apim %>%
  select(contains("Depression") & contains("Mother") & contains("item")) %>%
  names()

depression_dad <- small_apim %>%
  select(contains("Depression") & contains("Father") & contains("item")) %>%
  names()

## Coparent
coparent_mom <- small_apim %>%
  select(contains("Coparent") & contains("Mother") & contains("item")) %>%
  names()

coparent_dad <- small_apim %>%
  select(contains("Coparent") & contains("Father") & contains("item")) %>%
  names()

## CBCL
cbcl_kid <- small_emoreg %>%
  select(contains("CBCL") & !contains("Total")) %>%
  names()

sect_properties <- prop_section(page_size = page_size(orient = "landscape"))
```

## APIM

### Depression Mother

```{r}
# Matrix 1
mice_alpha(imp = apimsmall.mi1,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi1alpha_depressionmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi1,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi1alpha_depressionmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi1,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi1alpha_depressionmom.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = apimsmall.mi2,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi2alpha_depressionmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi2,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi2alpha_depressionmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi2,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi2alpha_depressionmom.docx", 
               pr_section = sect_properties)

# Matrix 3
mice_alpha(imp = apimsmall.mi3,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi3alpha_depressionmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi3,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi3alpha_depressionmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi3,
           varlist = depression_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi3alpha_depressionmom.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_apim %>%
  select(all_of(depression_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/smallapimalpha_depressionmom.docx", 
               pr_section = sect_properties)

delete <- medium_apim %>%
  select(all_of(depression_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/mediumapimalpha_depressionmom.docx", 
               pr_section = sect_properties)

delete <- large_apim %>%
  select(all_of(depression_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/largeapimalpha_depressionmom.docx", 
               pr_section = sect_properties)

delete <- original_apim %>%
  select(all_of(depression_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/originalapimalpha_depressionmom.docx", 
               pr_section = sect_properties)
```

### Depression Father

```{r}
# Matrix 1
mice_alpha(imp = apimsmall.mi1,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi1alpha_depressiondad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi1,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi1alpha_depressiondad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi1,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi1alpha_depressiondad.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = apimsmall.mi2,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi2alpha_depressiondad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi2,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi2alpha_depressiondad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi2,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi2alpha_depressiondad.docx", 
               pr_section = sect_properties)

# Matrix 3
mice_alpha(imp = apimsmall.mi3,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi3alpha_depressiondad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi3,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi3alpha_depressiondad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi3,
           varlist = depression_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi3alpha_depressiondad.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_apim %>%
  select(all_of(depression_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/smallapimalpha_depressiondad.docx", 
               pr_section = sect_properties)

delete <- medium_apim %>%
  select(all_of(depression_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/mediumapimalpha_depressiondad.docx", 
               pr_section = sect_properties)

delete <- large_apim %>%
  select(all_of(depression_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/largeapimalpha_depressiondad.docx", 
               pr_section = sect_properties)

delete <- original_apim %>%
  select(all_of(depression_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/originalapimalpha_depressiondad.docx", 
               pr_section = sect_properties)
```

### Coparent Mother

```{r}
# Matrix 1
mice_alpha(imp = apimsmall.mi1,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi1alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi1,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi1alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi1,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi1alpha_coparentmom.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = apimsmall.mi2,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi2alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi2,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi2alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi2,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi2alpha_coparentmom.docx", 
               pr_section = sect_properties)

# Matrix 3
mice_alpha(imp = apimsmall.mi3,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi3alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi3,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi3alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi3,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi3alpha_coparentmom.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_apim %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/smallapimalpha_coparentmom.docx", 
               pr_section = sect_properties)

delete <- medium_apim %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/mediumapimalpha_coparentmom.docx", 
               pr_section = sect_properties)

delete <- large_apim %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/largeapimalpha_coparentmom.docx", 
               pr_section = sect_properties)

delete <- original_apim %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/originalapimalpha_coparentmom.docx", 
               pr_section = sect_properties)
```

## Coparent Father

```{r}
mice_alpha(imp = apimsmall.mi1,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi1alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi1,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi1alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi1,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi1alpha_coparentdad.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = apimsmall.mi2,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi2alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi2,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi2alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi2,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi2alpha_coparentdad.docx", 
               pr_section = sect_properties)

# Matrix 3
mice_alpha(imp = apimsmall.mi3,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/smallmi3alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimmedium.mi3,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/mediummi3alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = apimlarge.mi3,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/apim/imputed_output/largemi3alpha_coparentdad.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_apim %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/smallapimalpha_coparentdad.docx", 
               pr_section = sect_properties)

delete <- medium_apim %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/mediumapimalpha_coparentdad.docx", 
               pr_section = sect_properties)

delete <- large_apim %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/largeapimalpha_coparentdad.docx", 
               pr_section = sect_properties)

delete <- original_apim %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/apim/nonimputed_output/originalapimalpha_coparentdad.docx", 
               pr_section = sect_properties)
```

## Emo Reg

### Coparent Mom

```{r}
# Matrix 1
mice_alpha(imp = emoregsmall.mi1,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi1alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoregmedium.mi1,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi1alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoreglarge.mi1,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi1alpha_coparentmom.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = emoregsmall.mi2,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi2alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoregmedium.mi2,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi2alpha_coparentmom.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoreglarge.mi2,
           varlist = coparent_mom,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi2alpha_coparentmom.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_emoreg %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/smallemoregalpha_coparentmom.docx", 
               pr_section = sect_properties)

delete <- medium_emoreg %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/mediumemoregalpha_coparentmom.docx", 
               pr_section = sect_properties)

delete <- large_emoreg %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/largeemoregalpha_coparentmom.docx", 
               pr_section = sect_properties)

delete <- original_emoreg %>%
  select(all_of(coparent_mom)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/originalemoregalpha_coparentmom.docx", 
               pr_section = sect_properties)
```

## Coparent Father

```{r}
mice_alpha(imp = emoregsmall.mi1,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi1alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoregmedium.mi1,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi1alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoreglarge.mi1,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi1alpha_coparentdad.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = emoregsmall.mi2,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi2alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoregmedium.mi2,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi2alpha_coparentdad.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoreglarge.mi2,
           varlist = coparent_dad,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi2alpha_coparentdad.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_emoreg %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/smallemoregalpha_coparentdad.docx", 
               pr_section = sect_properties)

delete <- medium_emoreg %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/mediumemoregalpha_coparentdad.docx", 
               pr_section = sect_properties)

delete <- large_emoreg %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/largeemoregalpha_coparentdad.docx", 
               pr_section = sect_properties)

delete <- original_emoreg %>%
  select(all_of(coparent_dad)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/originalemoregalpha_coparentdad.docx", 
               pr_section = sect_properties)
```

### CBCL

```{r}
mice_alpha(imp = emoregsmall.mi1,
           varlist = cbcl_kid,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi1alpha_cbclkid.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoregmedium.mi1,
           varlist = cbcl_kid,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi1alpha_cbclkid.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoreglarge.mi1,
           varlist = cbcl_kid,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi1alpha_cbclkid.docx", 
               pr_section = sect_properties)

# Matrix 2
mice_alpha(imp = emoregsmall.mi2,
           varlist = cbcl_kid,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/smallmi2alpha_cbclkid.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoregmedium.mi2,
           varlist = cbcl_kid,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/mediummi2alpha_cbclkid.docx", 
               pr_section = sect_properties)

mice_alpha(imp = emoreglarge.mi2,
           varlist = cbcl_kid,
           bnum = 1e4) %>% 
  save_as_docx(path = "2_output/emoreg/imputed_output/largemi2alpha_cbclkid.docx", 
               pr_section = sect_properties)
```

```{r}
delete <- small_emoreg %>%
  select(all_of(cbcl_kid)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/smallemoregalpha_cbclkid.docx", 
               pr_section = sect_properties)

delete <- medium_emoreg %>%
  select(all_of(cbcl_kid)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/mediumemoregalpha_cbclkid.docx", 
               pr_section = sect_properties)

delete <- large_emoreg %>%
  select(all_of(cbcl_kid)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/largeemoregalpha_cbclkid.docx", 
               pr_section = sect_properties)

delete <- original_emoreg %>%
  select(all_of(cbcl_kid)) %>%
  psych::alpha(impute = "mean")
delete$total %>% as.data.frame() %>% df2flextable() %>% 
  save_as_docx(path = "2_output/emoreg/nonimputed_output/originalemoregalpha_cbclkid.docx", 
               pr_section = sect_properties)
```

# Missingness

```{r}
# plot_pattern(original_apim)
```

# Predictor Matrices

## APIM

```{r}
apim_pred1 <- plot_pred(
  apimsmall.mi1$predictorMatrix, 
  label = TRUE, 
  rotate = FALSE,
  square = FALSE) + scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank())
ggsave(plot = apim_pred1, filename = "2_output/apim/imputed_output/apimpred_matrix1.tiff",
        height = 6, width = 8, units = "in")

apim_pred2 <- plot_pred(
  apimsmall.mi2$predictorMatrix, 
  label = TRUE, 
  rotate = TRUE,
  square = FALSE) + scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank())
ggsave(plot = apim_pred2, filename = "2_output/apim/imputed_output/apimpred_matrix2.tiff",
        height = 6, width = 8, units = "in")

apim_pred3 <- plot_pred(
  apimsmall.mi3$predictorMatrix, 
  label = TRUE, 
  rotate = TRUE,
  square = FALSE) + scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank())
ggsave(plot = apim_pred3, filename = "2_output/apim/imputed_output/apimpred_matrix3.tiff",
        height = 6, width = 8, units = "in")
```

## Emo Reg

```{r}
emoreg_pred1 <- plot_pred(
  emoregsmall.mi1$predictorMatrix, 
  label = TRUE, 
  rotate = TRUE,
  square = FALSE) + scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank())
ggsave(plot = emoreg_pred1, filename = "2_output/emoreg/imputed_output/emoregpred_matrix1.tiff",
        height = 8, width = 10, units = "in")

emoreg_pred2 <- plot_pred(
  emoregsmall.mi2$predictorMatrix, 
  label = TRUE, 
  rotate = TRUE,
  square = FALSE) + scale_fill_manual(values = c("white", "red")) +
  theme(axis.text.x.top = element_blank(),
        axis.ticks.x.top = element_blank())
ggsave(plot = emoreg_pred2, filename = "2_output/emoreg/imputed_output/emoregpred_matrix2.tiff",
        height = 8, width = 10, units = "in")
```

# Missingness

## APIM

```{r}
options(width = 100)
apimsmall.mi1$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimsmallmi1_loggedEvents.txt")

options(width = 100)
apimmedium.mi1$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimmediummi1_loggedEvents.txt")

options(width = 100)
apimlarge.mi1$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimlargemi1_loggedEvents.txt")

# Matrix 2
options(width = 100)
apimsmall.mi2$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimsmallmi2_loggedEvents.txt")

options(width = 100)
apimmedium.mi2$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimmediummi2_loggedEvents.txt")

options(width = 100)
apimlarge.mi2$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimlargemi2_loggedEvents.txt")

# Matrix 3
options(width = 100)
apimsmall.mi3$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimsmallmi3_loggedEvents.txt")

options(width = 100)
apimmedium.mi3$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimmediummi3_loggedEvents.txt")

options(width = 100)
apimlarge.mi3$loggedEvents %>%
  write.table(file = "2_output/apim/imputed_output/apimlargemi3_loggedEvents.txt")
```

## Emo Reg

```{r}
# Matrix 1
options(width = 100)
emoregsmall.mi1$loggedEvents %>%
  write.table(file = "2_output/emoreg/imputed_output/emoregsmallmi1_loggedEvents.txt")

options(width = 100)
emoregmedium.mi1$loggedEvents %>%
  write.table(file = "2_output/emoreg/imputed_output/emoregmediummi1_loggedEvents.txt")

options(width = 100)
emoreglarge.mi1$loggedEvents %>%
  write.table(file = "2_output/emoreg/imputed_output/emoreglargemi1_loggedEvents.txt")

# Matrix 2
options(width = 100)
emoregsmall.mi2$loggedEvents %>%
  write.table(file = "2_output/emoreg/imputed_output/emoregsmallmi2_loggedEvents.txt")

options(width = 100)
emoregmedium.mi2$loggedEvents %>%
  write.table(file = "2_output/emoreg/imputed_output/emoregmediummi2_loggedEvents.txt")

options(width = 100)
emoreglarge.mi2$loggedEvents %>%
  write.table(file = "2_output/emoreg/imputed_output/emoreglargemi2_loggedEvents.txt")
```
